Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-22 Ben_Manuscripts/structure_paper/Draft.tex
Modifications for paper

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (See supporting information). 
  %BJC5: section showing self-assembly set up to be added
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  %BJC5: perhaps this paragraph should be moved to supporting info.
  We developed the algorithm based on the known reaction mechanism.
  Cross-linking of this system is a free radical polymerization (FRP) taking
  place between terminal vinyl groups present on each of the three monomer tails.
  FRPs require an initiator which bonds to the system, meaning new atoms are
  introduced into the system. For simplicity, we simulated the initiator as
  hydrogen and made it present in the simulation by including them as dummy atoms
  in all possible locations where an addition could occur. We carry out the
  cross-linking procedure iteratively. During each iteration, the algorithm
  selects eligible bonding carbon atoms based on a distance cut-off. The topology
  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
  hydrogen types.  Head-to-tail addition was the only propagation mode considered
  due to its dominance in the real system \cite{young_introduction_2011}. We did
  not consider direction of attack because the resultant mixture is racemic.

  Our implementation requires long simulation times to achieve high cross-link 
  densities. A typical cross-linking procedure can take up to 24 hours. In
  order to collect equilibrated data, further NPT simulation is necessary. We
  typically run a cross-linked system for an additional 100 ns to allow the system
  to readjust. For those reasons we did not cross-link all systems tested, but only
  the most promising structure. We show that cross-linking does not significantly
  change any of our drawn conclusions in Section 3.6.

@@

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will converge to
  a single equilibrium configuration. For simplicity, we will group the systems studied here into
  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
  ordered basin and any system where $\mathit{d}=5.0$ \AA will be included in the disordered basin.
  The reason for these names will become clearer as we progress through our analysis.

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We generated simulated patterns using portions of simulation trajectory after
  equilibration. The patterns for all structures are shown and compared to experiment
  in Figure~\ref{fig:XRDsim}.

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. R-double does not appear in any
  of the patterns.

@@

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. Table 
  ~\ref{table:relative_inensities_300K} quantifies the relative intensity of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1.
  % BJC5: show how intensities are measured in supporting info
  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
  significantly higher than experiment in our simulations. R-spots is measured as the average
  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
  inspection. If the spots were not easily discernable, then the intensity was taken as that of
  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
  cases. There is no R-double intensity to be measured. Descriptive figures are provided in the
  supporting information to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the $q_z$ axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations. Unfortunately,
  our simulations are not long enough to sample enough independent configurations. Increasing the
  number of trajectory frames used to simulate the structure factor within a given interval of time
  does not offer any improvement.
  %BJC5: maybe show in supplemental?

@@

  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails and measured the angle between each centroid and its
  nearest neighbors with respect to the plane of the membrane. We see distinct
  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).

@@

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section TBD of the supporting information for illustrative examples. 
  % BJC5: Trying using inverted fourier transform of 2D experimental waxs. See what z-cross-section
  % looks like (does it oscillate more or less?) Then take FT of that and compare its intensity
  % to simulated intensity

@@

  We observe unusually slow dynamics in our system relative to other liquid crysal
  systems. Typical diffusion constants for columnar liquid crystals have been reported
  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
  constants of monomers in each of the systems we studied (See Table~\ref{S-table:msd}
  in Supporting Information) and learned that they are all on the order of $10^{-14}~m^2/s$.
  Our systems may be frozen in a glassy state. It is also possible that we are simply 
  observing characteristics of the experimental system. There has been no experimental work
  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
  system and no measurement of the glass transition temperature. Such a low
  diffusion constant is not unheard of. A more recent study reported a diffusion
  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.

@@

  We quantified the movement of the tails during our simulations by calculating the 
  autocorrelation function of the dihedral angle formed around the bond between the 
  head groups and the ether oxygens which attach the tails to the head group. 
  %BJC5: add diagram of which oxygens I'm talking about to the supporting info.
  We exclude the dihedral from the middle tail since it is fundamentally different
  than the two symmetric outside tails.

  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
  function plateau's near a value of -0.2 which indicates that the tails are starting in 
  an unfavorable configuration. We implemented distance restraints between the centers of 
  mass of monomer head groups to preserve the hexagonal phase (see Supporting Information
  %BJC5: supporting info section on this doesn't exist yet.
  for further detail), then rose the temperature of the equilibrated 300 K system to 500 K.
  We witnessed decorrelation of tails after $\approx$ 11 ns with a plateau at 0, 
  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed the 
  resultant configuration back down to 300 K to see if the increased rotational freedom 
  might allow the system to relax into to a more tightly packed configuration.
  %BJC5: more to come.

@@

  We explored the affect of water on pore structure, addressing question
  (\ref{point:water}), by preparing parallel displaced and sandwiched
  configurations according to the wet equilibration procedure. We limit
  the discussion to the ordered pore basin since it produces equilibrated 
  configurations closest to experiment. There is no experimental measurement
  of trace water concentration in these membranes so we tested
  a range of water concentrations from 1 to 5 percent. Figure~\ref{fig:solvation}
  shows the simulated diffraction patterns resulting from each configuration.

@@

  We used equilibrated systems in the ordered pore basin to calculate ionic 
  conductivity since we believe its structure is the closest match to
  experiment. Our models give reasonable estimates of ionic conductivity when
  compared to experiment. We compare calculated values of ionic conductivity
  obtained using the Nernst-Einstein relation and Collective Diffusion model in
  % names of equations capitalized?
  Figure~\ref{fig:conductivity}. The two methods agree with each other within
  error, although the uncertainty obtained using the Collective Diffusion model
  is much higher. We require much longer simulations to lower the uncertainty,
  however it is not feasible to do so with a large system. We will only use the
  Nernst-Einstein relation in future calculations of this type.

@@

  The system's structure and physical characteristics did not change
  significantly when we applied the cross-linking algorithm to the equilibrated
  parallel-displaced configuration in the ordered pore basin. We simulated
  the cross-linked system in the NPT ensemble for 100 ns. After the system is
  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
  between layers increases by 0.04 \AA. All major features are still present in
  the simulated XRD patterns, however at lower intensities
  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
  Nernst-Einstein relation and found that it is lower in the cross-linked system
  (Fig.~\ref{fig:IC_xlink}).
  %BJC: The current XRD pattern is from a 100 ns simulation. I am running it out
  % longer to get more statistics

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{IC_xlink.png}
	\caption{}~\label{fig:IC_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{dbwl_xlink.png}
	\caption{}~\label{fig:dbwl_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{p2p_xlink.png}
	\caption{}~\label{fig:p2p_xlink}
  \end{subfigure}
  \caption{Applying our simulated crosslinking mechanism to an equilibrium
	  configuration causes slight changes to the system's physical and structural
	  properties. (a) Reflections produced by the cross-linked configuration are
	  faded relative to the uncross-linked system. (b) The ionic conductivity is
	  smaller relative to the uncross-linked system, but still much larger than the
	  experimental value. When the system is cross-linked, the distance between
	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
  \end{figure}

>>>>

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (See section S~\ref{S-section:self_assembly}). 
  %BJC5: section showing self-assembly set up to be added
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  %BJC5: perhaps this paragraph should be moved to supporting info.
  We developed the algorithm based on the known reaction mechanism.
  Cross-linking of this system is a free radical polymerization (FRP) taking
  place between terminal vinyl groups present on each of the three monomer tails.
  The reaction mechanism is drawn out in Figure S-\ref{S-fig:xlink_mech}.
  FRPs require an initiator which bonds to the system, meaning new atoms are
  introduced into the system. For simplicity, we simulated the initiator as
  hydrogen and made it present in the simulation by including them as dummy atoms
  in all possible locations where an addition could occur. We carry out the
  cross-linking procedure iteratively. During each iteration, the algorithm
  selects eligible bonding carbon atoms based on a distance cut-off. The topology
  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
  hydrogen types.  Head-to-tail addition was the only propagation mode considered
  due to its dominance in the real system \cite{young_introduction_2011}. We did
  not consider direction of attack because the resultant mixture is racemic.

  Our implementation requires long simulation times to achieve high cross-link 
  densities. A typical cross-linking procedure can take up to 24 hours. In
  order to collect equilibrated data, further NPT simulation is necessary. We
  typically run a cross-linked system for an additional 100 ns to allow the system
  to readjust. For those reasons we did not cross-link all systems tested, but only
  the most promising structures. We show that cross-linking does not significantly
  change any of our drawn conclusions in Section 3.6.

@@

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will converge to
  a single equilibrium configuration. For simplicity, we will group the systems studied here into
  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
  ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
  The reason for these names will become clearer as we progress through our analysis.

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We extended each simulation by 100 ns in order to get more equilibrated 
  data. We generated simulated patterns using the extended of simulation trajectories
  The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. They are also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. Table 
  ~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1.
  % BJC5: show how intensities are measured in supporting info
  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
  significantly higher than experiment in our simulations. R-spots is measured as the average
  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
  inspection. If the spots were not easily discernable, then the intensity was taken as that of
  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
  cases. There is no R-double intensity to be measured. Figures are provided in 
  section S\ref{S-section:xrd_intensities} to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
  to sample enough independent configurations. Increasing the number of trajectory frames
  used to simulate the structure factor within a given interval of time does not offer 
  any improvement.

@@

  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails (Figure S-\ref{S-fig:centroids}) and measured the angle
  between each centroid and its nearest neighbors with respect to the plane of the 
  membrane. We see distinct peaks in the distribution of these angles 
  (Figure~\ref{fig:tail_packing}).

@@

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
  illustrative examples.

  The system size does not significantly alter the intensity of R-$\pi$. We equilibrated a 
  sandwiched system with twice as many monomers per column so that the system size doubled in 
  the z-direction. The correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA, 
  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
  are nearly identical (See Figure~\ref{S-fig:z_correlation_overlay}).

@@

  We observe unusually slow dynamics in our system relative to other liquid crysal
  systems. Typical diffusion constants for columnar liquid crystals have been reported
  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
  constants of monomers in each of the systems we studied (See Table S-\ref{S-table:msd}) 
  and learned that they are all on the order of $10^{-14}~m^2/s$.
  Our systems may be frozen in a glassy state. It is also possible that we are simply 
  observing characteristics of the experimental system. There has been no experimental work
  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
  system and no measurement of the glass transition temperature. Such a low
  diffusion constant is not unheard of. A more recent study reported a diffusion
  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.

@@

  We quantified the movement of the tails during our simulations by calculating the 
  autocorrelation function of the dihedral angle formed around the bond between the 
  head groups and the ether oxygens which attach the tails to the head group 
  (See Figure S\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
  since it is fundamentally different than the two symmetric outside tails. We 
  limited these studies to the sandwiched configuration for simplicity.

  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
  function plateau's near a value of -0.2 which indicates that the tails are starting in 
  an unfavorable configuration. We implemented distance restraints between the centers of 
  mass of monomer head groups to preserve the hexagonal phase, then rose the temperature 
  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
  decorrelation of ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
  freedom might allow the system to relax into to a more tightly packed configuration.

  Decorrelating the ether dihedrals at high temperature, followed by thermal annealing
  does not improve packing in our model. In the ideal case, if all monomers stacked 
  3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
  sandwiched system studied in this paper, the z-dimension of the unit cell equilibrated 
  to 8.87 nm, which is roughly consistent with the stacking distance reported in 
  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
  z-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
  course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
  annealing simulations may get the system to the correct density, but we do not have
  the resources to further explore this approach. 
  % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
  % is because the initial box z-box dimension is ~10.9. In the 500K system, the initial
  % z-box dimension is ~9.7

@@

  We explored the effect of water on pore structure, addressing question
  (\ref{point:water}), by preparing parallel displaced and sandwiched
  configurations according to the wet equilibration procedure. We limit
  the discussion to the ordered pore basin since it produces equilibrated 
  configurations closest to experiment. There is no experimental measurement
  of trace water concentration in these membranes so we tested
  a range of water concentrations from 1 to 5 percent. Figure~\ref{fig:solvation}
  shows the simulated diffraction patterns resulting from each configuration.

@@

  We used equilibrated systems in the ordered pore basin to calculate ionic 
  conductivity since we believe their structures are the closest match to
  experiment. Our models give reasonable estimates of ionic conductivity when
  compared to experiment. We compare calculated values of ionic conductivity
  obtained using the Nernst-Einstein relation and Collective Diffusion model in
  % names of equations capitalized?
  Figure~\ref{fig:conductivity}. The two methods agree with each other within
  error, although the uncertainty obtained using the Collective Diffusion model
  is much higher. We require much longer simulations to lower the uncertainty,
  however it is not feasible to do so with a large system. We will only use the
  Nernst-Einstein relation in future calculations of this type.

@@

  We applied our crosslinking algorithm to equilibrated sandwiched and parallel
  displaced configurations in the ordered pore basin. We allowed the crosslinking
  algorithm to propagate until greater than 90 \% of vinyl groups were either involved
  in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
  for further details on the crosslinking algorithm. We allowed the crosslinked
  configurations to simulate for 100 ns further in the NPT ensemble.

  % BJC5: Is it worth including the distance between layers and the correlation length?   
  There are minor changes to the physical characteristics of these systems when 
  they are crosslinked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
  the sandwiched configuration decreases while that of the parallel displaced 
  configuration stays the same. The pore spacing decreases in both systems by
  0.07 nm. The vertical monomer stacking distance increases in the sandwiched
  configuration and decreases in the parallel displaced configuration, however the 
  values of crosslinked configurations fall within uncertainty of their un-crosslinked
  counterparts. The correlation length decreases in both systems, but is most 
  pronounced in the parallel displaced system.

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{xlink_charts.eps}
  \caption{There are minor differences between the physical properties of a
  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
  configuration remains constant. The pore spacing of both systems decreases upon crosslinking.
  The vertical distance between stacked monomers increases in the sandwiched configuration
  and decreases in the parallel displaced configuration. The correlation length decreases
  in both configurations.}\label{fig:xlink}
  \end{figure}

%  The system's structure and physical characteristics did not change
%  significantly when we applied the cross-linking algorithm to the equilibrated
%  parallel-displaced configuration in the ordered pore basin. We simulated
%  the cross-linked system in the NPT ensemble for 100 ns. After the system is
%  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
%  between layers increases by 0.04 \AA. All major features are still present in
%  the simulated XRD patterns, however at lower intensities
%  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
%  Nernst-Einstein relation and found that it is lower in the cross-linked system
%  (Fig.~\ref{fig:IC_xlink}).

%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{rzplot_xlink.png}
%	\caption{}~\label{fig:rzplot_xlink}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{IC_xlink.png}
%	\caption{}~\label{fig:IC_xlink}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{dbwl_xlink.png}
%	\caption{}~\label{fig:dbwl_xlink}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{p2p_xlink.png}
%	\caption{}~\label{fig:p2p_xlink}
%  \end{subfigure}
%  \caption{Applying our simulated crosslinking mechanism to an equilibrium
%	  configuration causes slight changes to the system's physical and structural
%	  properties. (a) Reflections produced by the cross-linked configuration are
%	  faded relative to the uncross-linked system. (b) The ionic conductivity is
%	  smaller relative to the uncross-linked system, but still much larger than the
%	  experimental value. When the system is cross-linked, the distance between
%	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
%  \end{figure}
